Hydra Battles and Cie

### 2021-01-22 doc/part-hydras.tex
comments and examples about the Ackermann part (to continue)
add an exercise

\index{Coq!Techniques!Mutually inductive types}
\index{Coq!Commands!Scheme}

@@

% \label{warning:coercions}
% \index{Coq!Techniques!Coercions} 
% \begin{remark}
% Beware of coercions and notation scopes!
% Let us consider the following goal:

@@

\index{Exercises}
\begin{exercise}
Prove, that, in any ordinal notation system, that every ordinal has at most one predecessor, and at most one successor. 
\end{exercise}

\index{Exercises}
\begin{exercise}
Prove, that, in any ordinal notation system, that if $\beta$ is a successor of $\alpha$,
then for any $\gamma$, $\gamma<\beta$ implies 
$\gamma\leq\alpha$.
\end{exercise}

@@

\index{Coq!Techniques!Unicity of equality proofs}
\label{sect:eq-proof-unicity}

@@

% \index{Coq!Techniques!Coercions}
% \index{Functions!Coercions@Coercions (from nat to ordinal types)}
% \begin{remark}
% Please refer to the remark~\pageref{warning:coercions} about the use of coercions.
% % The use of coercions like \texttt{fin} allow us to be close to the mathematical tradition where natural numbers are ordinals too.
% % Nevertheless, it may happen that a goal like \texttt{3 < 5} could be 
% % interpreted as \texttt{(lt (fin 3) (fin 5))},  depending on the current notation scope.  
% % When this misinterpretation happens, tactics like \texttt{auto with arith}, \texttt{lia} do not work!
% % Thus, it is useful to write \texttt{(3 < 5)\%nat}  an inequality between two natural numbers. 
% \end{remark}

@@

\index{Coq!Techniques!Unicity of equality proofs}

@@

\begin{exercise}
Prove that the \emph{total} order \texttt{lt} on \texttt{T1} is not well-founded. 
\textbf{Hint:}  You will have to build a counter-example with terms of type \texttt{T1}
which are not in Cantor normal form.
\end{exercise}

@@

\subsubsection{A First Attempt}
\label{sec:orgheadline77}
\index{Coq!Techniques!Well-founded induction}

@@

\textbf{Hint:} You may add to your function a third argument usually called \texttt{fuel} for allowing you to give a structurally 
recursive function (\emph{cf} the post of Guillaume Melquiond on Coq-club (Dec 21, 2020)
\url{https://sympa.inria.fr/sympa/arc/coq-club/2020-12/msg00069.html}).
The type \texttt{fuel}, an alternative 
to \texttt{nat} is available on \href{../theories/html/hydras.Prelude.Fuel.html}{Prelude.Fuel}).
\index{Coq!Techniques!Giving fuel to a long computation}

@@

\label{lemma:L-2_6-1}
\index{Coq!Techniques!Sigma types}

@@

\index{Coq!Techniques!Transfinite induction}

>>>>

\index{Coq!Mutually inductive types}
\index{Coq!Commands!Scheme}

@@

% \label{warning:coercions}
% \index{Coq!Coercions} 
% \begin{remark}
% Beware of coercions and notation scopes!
% Let us consider the following goal:

@@

\index{Exercises}
\begin{exercise}
Prove, that, in any ordinal notation system, every ordinal has at most one predecessor, and at most one successor.

\emph{You may start this exercise with the file
\url{../exercises/ordinals/predSuccUnicity.v}.}

\index{Exercises}
\begin{exercise}
Prove, that, in any ordinal notation system, if $\beta$ is a successor of $\alpha$,
then for any $\gamma$, $\gamma<\beta$ implies 
$\gamma\leq\alpha$.
\end{exercise}

@@

\index{Coq!Unicity of equality proofs}
\label{sect:eq-proof-unicity}

@@

% \index{Coq!Coercions}
% \index{Functions!Coercions@Coercions (from nat to ordinal types)}
% \begin{remark}
% Please refer to the remark~\pageref{warning:coercions} about the use of coercions.
% % The use of coercions like \texttt{fin} allow us to be close to the mathematical tradition where natural numbers are ordinals too.
% % Nevertheless, it may happen that a goal like \texttt{3 < 5} could be 
% % interpreted as \texttt{(lt (fin 3) (fin 5))},  depending on the current notation scope.  
% % When this misinterpretation happens, tactics like \texttt{auto with arith}, \texttt{lia} do not work!
% % Thus, it is useful to write \texttt{(3 < 5)\%nat}  an inequality between two natural numbers. 
% \end{remark}

@@

\index{Coq!Unicity of equality proofs}

@@

\begin{exercise}
Prove that the \emph{total} order \texttt{lt} on \texttt{T1} is not well-founded. 
\textbf{Hint:}  You will have to build a counter-example with terms of type \texttt{T1}
which are not in Cantor normal form.

\emph{You may start this exercise with the file
\url{../exercises/ordinals/T1_ltNotWf.v}.}
\end{exercise}

@@

\subsubsection{A First Attempt}
\label{sec:orgheadline77}
\index{Coq!Well-founded induction}

@@

\textbf{Hint:} You may add to your function a third argument usually called \texttt{fuel} for allowing you to give a structurally 
recursive function (\emph{cf} the post of Guillaume Melquiond on Coq-club (Dec 21, 2020)
\url{https://sympa.inria.fr/sympa/arc/coq-club/2020-12/msg00069.html}).
The type \texttt{fuel}, an alternative 
to \texttt{nat} is available on \href{../theories/html/hydras.Prelude.Fuel.html}{Prelude.Fuel}).
\index{Coq!Giving fuel to a long computation}

@@

\label{lemma:L-2_6-1}
\index{Coq!Sigma types}

@@
